This document represents a synthetic study of the work carried out in part of my second-year summer internship. I did my internship within
the international university of Rabat \textbf{UIR} and the Directorate General of Territorial Communities (Directorate of Urban Mobility and Transport) under the Ministry of the Interior \textbf{DGCT}. This internship lasted both
the months of July and August of the year 2021. The main objective of this work
consists of developing a web platform for the management and monitoring of
contracts for the delegated management of urban bus transport. The project was carried out in three main stages:
\begin{itemize}
    \item[•] detailed analysis of customer needs;
    \item[•] design of the different components of the application;
    \item[•] finally the implementation of the underlined objectives.
\end{itemize}
So I had the chance to use several technologies, tools, and concepts that helped me develop this solution, including several courses that I learned during the previous year, and some tools that I had the chance to discover throughout the internship (you will find in the appendices of this document).

This report is organized as follows: Chapter I is dedicated to
the presentation of
the host organization and the client. Chapter II deals with
the analysis of the problem as well as the specification of the needs.
Chapter III presents the conceptual study, and finally chapter IV deals with the
realization part.

\textbf{\\Keywords:\\Management, Monitoring, Data, Bus, Delegated monitoring, contracts, Urban transport, Centralization, Low-code application.}
